Exploratory Data Analysis for College Scorecard Dataset

### 2017-02-22 Draft-xuezhou-sjb.Rmd
fix

###5.1.5 Earning<a id="5.1.5"></a> 
####5.1.5.1 Median family income in real 2015 dollars<a id="5.1.5.1"></a>
This element is recorded the median family income of students, one of the undergraduate student demographics for earnings cohorts. We are using the code below to summarize this variable.

@@

##6.9 The Relashionship between the Default Rate of Loan Repayment and Post-graduation Earnings<a id="6.9"></a> 
For one thing, understanding the relationship between the default rate of loan repayment and post-graduation earnings can help federal financial committee to improve their decisions about load granting. If the default rate decreases as the earnings increases, the committee may prefer to grant more financial aid to institutions whose students have higher earnings. For another, the default rate of repayment for a university can also help predict the post-graduation earnings for its students.

@@

##6.10 The Relashionship between Earning 6 Years from Entry and Degree Type<a id="6.10"></a>

@@

##6.11 The Relashionship among Predominant Degree, Control and Earning after 6 year of Entry<a id="6.11"></a>

@@

##6.12 The Relashionship between Predominant Degree and Control<a id="6.12"></a>

@@

##6.13 The Relashionship between Control and Median earnings of Students Working and Not Enrolled 6 Years after Entry<a id="6.13"></a>

>>>>

###5.1.5 Earning<a id="5.1.5"></a> 
####5.1.5.1 Median family income in real 2015 dollars<a id="5.1.5.1"></a>
This element is recorded the median family income of students, one of the undergraduate student demographics for earnings cohorts. We are using the code below to summarize this variable(min, max, mean, median and standard deviation).

@@

##6.9 The Relationship between the Default Rate of Loan Repayment and Post-graduation Earnings<a id="6.9"></a> 
For one thing, understanding the relationship between the default rate of loan repayment and post-graduation earnings can help federal financial committee to improve their decisions about load granting. If the default rate decreases as the earnings increases, the committee may prefer to grant more financial aid to institutions whose students have higher earnings. For another, the default rate of repayment for a university can also help predict the post-graduation earnings for its students.

@@

##6.10 The Relationship between Earning 6 Years from Entry and Degree Type<a id="6.10"></a>

@@

##6.11 The Relationship among Predominant Degree, Control and Earning after 6 year of Entry<a id="6.11"></a>

@@

##6.12 The Relationship between Predominant Degree and Control<a id="6.12"></a>

@@

##6.13 The Relationship between Control and Median earnings of Students Working and Not Enrolled 6 Years after Entry<a id="6.13"></a>
